\documentclass[12pt,openany]{memoir}
\usepackage{graphicx}
\usepackage{amsmath,amssymb}

\DeclareFontFamily{U}{rcjhbltx}{}
\DeclareFontShape{U}{rcjhbltx}{m}{n}{<->rcjhbltx}{}
\DeclareSymbolFont{hebrewletters}{U}{rcjhbltx}{m}{n}

% remove the definitions from amssymb
\let\aleph\relax\let\beth\relax
\let\gimel\relax\let\daleth\relax

\DeclareMathSymbol{\aleph}{\mathord}{hebrewletters}{39}
\DeclareMathSymbol{\beth}{\mathord}{hebrewletters}{98}\let\bet\beth

\title{Something About Blood}
\author{Andy Modell}

\begin{document}
\maketitle
\chapter*{Preface to the Second Edition}

It is with great honor that I, Frilio Rolthnor of Petoskey, do at last submit to Librarian of Congress, Stewart R. Williams, this manuscript for the second edition of my history of the notable events surrounding <main> <lastname> that took place between the months of May 2036 CE and January 2037 CE.
While we understand that our previous edition had been met with much criticism and many recommendations from the Editor of Congress, Oscar M. Pollock, it should be noted up front that all of the initially presented suggestions have been, regretably, ignored.
\\

We wish to be explicitly clear to Mr. Pollock that we in no way intend him any disrespect.
Who among us can doubt that without the suburb advice Mr. Pollock provided to E. Jones, her best selling \textit{A History of ``the Northwest Territories'', and All Lands Bearing Such a Name} would never had made its way onto the recommended reading lists in all but three of the school districts stationed in lands covered by the work.
It would be absurd to even consider whether the world would even know about T. J. Smith's international best seller \textit{Smith, from Profession to Name Across the World} had Oscar not provided Smith with the inspiration to shift the focus of this modern marvel beyond Tom's own home state of Virginia.
No.
We once more state explicitly and clearly that we wish no disrespect upon the artistic, linguistic, and stylistic abilities of our good friend Oscar.
His suggestions for revision have been all been very carefully and selectively ignored in the production of our second edition due to the offense that we took after his mocking of our name in front of the esteemed Librarian at the Winter Holidays Party where we last saw each other.
\\

Now that such disclosure has been presented, we shall denote the differences between this second edition and the first.
\\

It was much to our great surprise that, as you may be very well aware, the focus of most reviews for the initial publication seemed to be not on the history itself but the detail of which we described not only the sexual encounters surrounding and including our principal characters and their parents.
In an attempt to \textit{get back to the history}, we have removed all of such descriptions from this publication and we urge our readers to reconsider the significance of the history upon reading this rather than using it as material for such activities one may in the privacy of one's home.
\\

We also wish it to be known that all efforts have been spent in attempt to make this history more accessable to those who may not fancy a formal educational publication.  We have attempted and succeeded, though with much difficulty, to get the approval of my ninteen year old neffew regarding the level of entertainment and ease of reading this publication posesses.
\\

Once more, we would like to note that we did receive several additional suggestions to this edition by the esteemed Editor of Congress, Oscar Matthew Pollack, but those were deliberatly neglicted, and we even moved to remove our previously used pen-name from this edition in favor of our own out of spite.
\\

\chapter*{Preface to the First Edition}

It is with great honor that I, Wallace G. Cunningham of Petoskey, do at last submit to Librarian of Congress, Stewart R. Williams, this manuscript for my history of the notable events surrounding <main> <lastname> that took place between the months of May 2036 CE and January 2037 CE.
\\

As many of our readers must know, the events depicted in this work have been of the upmost significance in shaping both medical and economic policy of our country in the years since.
While many journalists have found it in their best interests to portray Mr. <lastname> as a sinister figure bent on destroying one of our countries great businesses, we pride our publication on its adherence to the spirit of the history.
Our work contains an adherence to primary sources unfound in modern texts that touch these events, and we pride ourselves on not excluding the interviews recorded of <lastname> in 2040 CE that so many of our fellow historians avoided due to the explicitness of the language and content.
As such, we believe that our work will provide the most accurate compiled sequence of these events published to date.
\\

We thank you, the reader, very much for your consideration of our volume, and we hope you take some degree of satisfaction with yourself upon completion of this work, for only then will you know the truth regarding <main> <lastname>'s story beyond what the popular media would have you believe.
\\

It should be noted that most characters featured in this work are based on real persons, and any dialogue based on their own.
At no time, however, did the author restrict himself to quotations provided by the individuals featured, and quotations used in this publication should not be interpreted as having been direct by the speakers.
If the reader would wish for a compilation of the source used in preparing this work, such a compilation may be found at the publishers website free of charge.
Should the publisher go out of business and lose its website, we have, in our possession, such a list, that we will attempt to distribute to the standard libraries in both print and electronic form.
\\

\chapter{}

Graduation couldn't have come soon enough.
<main> (A)'s friends had all warned him that more school after undergrad would drive him crazy, but <main> decided to ignore all this advice, and today it was finally over.  Having left the commencement ceremony a few hours prior, showered up, and met with his and Jake's family, <main> was now enjoying his graduation dinner at Frank's Steak House, where you certainly won't find any franks on the menu.
\\

Getting his Pharm D had been a long and arduous process.
It wasn't necessarily a difficult program, not for <main>, but having to stay in school four years after the majority of his friends had all gone off to the ``real world'' hadn't been easy.  Sure, Jake(A-) had been getting his PhD in Artificial Intelligence Systems here too, but it seemed like a rarity when Jake wasn't spending his nights in the lab trying to meet his paper deadlines or, later, finish his dissertation.  Still, <main> was passionate about his studies.  What could be more noble than working to produce medicines that could cure the ailments that still plague humanity today?
\\

Conversation at the table always seemed to take a rapid shift when <main> or Jake's mothers suddenly remarked, once again, how wonderful it was that they had \textit{two doctors} sitting with them now.
<main> always this was a silly notion.
His Pharm D and Jake's PhD made them no more doctors than <main>'s parents with their Juris Doctorits.
<mother>(A-) and <father>(AB+) <lastname> were both well known lawyers.
<mother>, his mother, fought hard in the Supreme Court case that resulted in the sending of encrypted messages, even those uncrackable by law enforcement, to be a protected right under the first amendment, while <father>, <main>'s father, had lead the team filing the patent on <cancer drug> back in 2019.
<cancer drug> was a marvolus piece of pharmaceutical magic; an annual injection of <cancer drug> will be sufficient to prevent the cells in 99.99\% of humanity from growing cancerous.
It was, of course, wildly popular now.
President Sanders even announced in his State of the Union address that the US had succeeded in curing cancer by the year 2020, as predicted.
Both of <main>'s parents were officially retired now, though <father> still spent his time in DC lobbying for <pharm>.
\\

Jake's parents (both A-) lead completely different routes.
While they were both certainly well off, both of Jake's parents had left the world of academia after their undergraduate degrees, so Jake was truly the first \textit{doctor} in their family.
Jake's parents had both worked at Microsoft back when Bill Gates was CEO, and Jake's mother had gone so far as to work with Mr. Gates himself on a secret project that never saw the light of day.
<main> had always been super jealous of this, since Bill Gates was his idol.
Microsoft never excited <main> too much, but what Gates did with his resources through the Gates Foundation after retiring was what really got <main> going.
Focusing on eliminating deadly diseases in parts of the world where resources were scarcest was the most noble of goals in <main>'s mind.
\\

``It's just so great to have two new doctors at the table!'' <mother> exclaimed again drawing giggles from Jake's mother and coordinated sighs from <main> and Jake.
``Oh, stop it now.
You two know how much you've worked for today.
Just think, the last time either of you weren't in school President Obama was still in his first term!''
\\

<mother> loved breaking down history based on presidential terms.
<main> and Jake were both twenty six even though <main> spent one fewer year on his Pharm D program than Jake on his PhD.
Due to an unanticipated set of moves between school districts on Jake's parents part, Jake had ended up skipping the second grade, so the two boys' getting their advanced degrees at the same time was a bit of a boon for the two families who had known each other since before two boys' shared birthday in September of 2010.
\\

``I'll toast to that!'' announced Jake raising his glass of \textit{whatever the darkest beer you have on tap}.
``To no more all-nighters preparing for exams or pulling off papers!''
\\

<main> was glad to toast to that.
While he never quite saw the sunrise while trying to prepare for his exams since undergrad, having to go home and write an essay after spending all day on his studies had always been <main>'s biggest complaint about school in general.
The opportunity to go home after a day of work with nothing to worry about besides whatever sport was in season would be wonderful.
\\

``Don't you two get optimistic on me now'' warned Jake's father.
\\

``Joe's right'' followed <father>, ``You're both moving out to Palo Alto.
If the \textit{culture} over in the valley is anything like it was when I was your age, you haven't escaped your late nights yet.
It's a very cutthroat work environment still.''
\\

``Here's to that'' continued Jake's mother clanking her Chardonnay against <father>'s Long Island Iced Tea.
``Even though you'll be working at <pharm> rather than in tech, you'll be spending long nights in the lab, no doubt'' she directed toward <main>.
\\

<main> and Jake had both managed to secure employment in Palo Alto after graduation, allowing them to continue sharing an apartment into the real world.
Jake had managed to get a job as an AI researcher at a company known for their self-driving cars, which were legal to drive in seven states and Norway.
<main>, on the other hand, got a job working as a researcher in one of <pharm>'s medicine labs.
<main> had made his father promise that no \textit{letters of recommendation} would end up influencing anything, but after acing a full day's set of interviews, <main> had secured the position on his own merit. Both boys agreed that the best time to start would be shortly after graduation, so this dinner was not only in celebration of their graduation, but also the last time either would be seeing their families again until Thanksgiving, half a year away.
\\

There wasn't too much more to talk about besides the slight change in lifestyle and graduation itself.
Both the boys had been financially independent since they finished undergrad, if you don't count <main>'s pharmacy school tuition, and not too much had happened with either of their families that hadn't been expressed earlier.
Neither <main> nor Jake had any remaining grandparents.
Those around at the time of O-Day hadn't managed last much longer.
Eventually, their food had come.
\\

All six at the table had ordered some sort of steak.
While they were ordering, <mother> had noted how good the salmon used to be at Frank's, but all mention of the dish had since vanished from the high-end steak house's menu.
It had come after a necessary re-branding campaign, but Frank's definitely still had the best food in town, and they lived up to their reputation.
The steaks were all cooked to perfection, and even <father>'s, which was ordered ``no pink'' had the juicy taste steak-lovers adore.
After their main courses, the six all shared what was Jake's favorite desert and Frank's special: the Brownie Sundae Pie.
\\

The Brownie Sundae Pie was a work of art, or so Jake would say.
Imagine an Oreo-cookie style pie crust filled with butter fudge ice cream from which one of each of Frank's signature brownies: (the peanut butter brownie, the peanut brownie, and the chocolate chunk brownie), all ascended to form a pyramid-like structure.
<father> was busy joking that the desert resembled some palace from the cover of a science fiction book he had read as a child as Jake immediately took a substantial slice of the pie to his plate containing a majority of the famed peanut butter brownie.
\\

After the delicious desert had been completed, <main> and Jake gave their final farewells to their parents and left to pack for the flight they had scheduled to California three days hence.
\\

\chapter{}

It followed, after the dinner which concluded in a desert so scrumptious sounding that describing it drew hunger into the mind of the author, that our friends, <main> and Jake, proceeded directly to their place of residence.
Having arrived at Frank's via a separate automobile than the ones used by their parents and having not consumed so much wine at dinner as to make it dangerous, <main> proceeded to drive himself and Jake back through streets of their college town, narrowly avoiding several of the severely intoxicated undergraduates in the midst of celebrating their own graduations, until they eventually reached their apartment over at 235 Maple St.
It occurred to <main>, as it often did upon his return to the building, that he'll probably never truly leave Maple St.
He was born in a hospital whose address was on a ``Maple St.'', and he had lived in an apartment on a different Maple St. at the institution where he got his undergraduate degree.
\\

The apartment itself wasn't anything special.
There were two bedrooms, both of comparable size, a single bathroom that needed dusting more frequently than any other room in the unit for some reason unknown to humankind, a kitchen of notable size, and a living room, which featured a pair of black leather sofas that Jake was quite fond of due to the staggeringly low investment needed to keep them clean.
There wasn't too much more for them to pack.
The all-school commencement ceremony took place several days after both the Pharmacy School and College of Computer Science's private ceremonies, so the two had alredy managed to get most of their belongings sorted out.
It was only the essentials that remained.
Well, the essentials and the entire kitchen.
\\

Sorting out the kitchen was a chore the two had been putting off for quite a few days.
Most everything useful in the kitchen, sans the boring-white appliances owned by the landlord and the hideous white tile counter tops, was a combination of items belonging to either the <lastname>s or Jake's family.
When a wok or a food processor was needed, one of the two knew where they could get one their parents wouldn't mind the absence of.
The sorting of such items would be a task that involved not only deciding what was worth shipping to California, but also determining, of the items not passed along, where those items would live the remainder of their lives.
\\

There was no trouble in some cases.  The non-stick pans had all come from Jake's mother, since she preferred to cook with her copper set nowadays, and the knives had all been hand-picked by <father> many years prior.
Cutlery and glassware were the real challenges.
In addition to trying to separate the forks, knives, and spoons into their respective sets, of which the boys identified three and a half, neither could remember whose parents' houses contained the matching siblings from which these collections had been separated.
Ultimately, the two had determined the origins of two but decided they could leave their parents with the tasks of ensuring the remaining piles got to their home drawers.
\\

At this time, a knocking could be heard coming from the door.
This was a simple door, and as such, the knocking fulfilled its purpose of informing the unit's residence about the existence of some individual creating the action.
Opening the door was a simple task for Jake, and as he had expected, the knocker was none other than Roland (A+).
This Roland, about whom we shouldn't go into too much detail, was a peculiar sort of person with with mid-length blond hair and glasses that somehow matched his lips.
Roland had a very specific purpose for knocking on the door of 235 Maple St, and this purpose was already known to <main> and Jake, for Roland had come to perform an exchange with the two boys of whom we've oh so recently left dinner with.
The exchange had been predetermined and was quite standard at this time of year.
A set of transfusions of Roland's blood, one to <main> and the second to Jake, in exchange for all the alcohol that the two had accumulated but not yet finished over the course of their graduate careers.
\\

The exchange took no time at all.
<main> had his Clencer 900, a marvolus piece of technology that could perform a direct vein-to-vein transfusion while filtering out everything unnecessary or likely to spread disease, prepared for the event, so after Roland surrendered all four MLs of his blood, two for <main> and two for Jake, he was well on his way with an assortment of hard liqors and beer bottles.
<main> and Jake had left no wine unfinished.
\\

Following this, each of the boys retired for the night in his own way.
<main> put on a white-noise machine and proceeded to dreamland, where he encountered a fascinating sport that involved attempting to bake cookies faster than an opponent could eat them, and Jake spent some time reading a book about four guardspeople saving their empire before he eventually dozed off himself.
\\

\chapter{}

At this time, we believe it is best to ensure our readers understand a matter of grave importance, an occurrence which has plagued the society that <main> and Jake inhabited.
These are attempts at word play, for we are, of course, talking about a plague which has, as you will soon know, lead many to their graves.
\\

At the beginning of the twenty first century, a culinary phenomenon began to spread across the wealthy developed world.
Beginning in ancient Japan, the art of sushi making, and subsequent eating, became ever increasingly popular due to the excellent flavors and perceived health benefits of the artfully created dishes.
Sushi, for those of you who may now know of this all-but-forgotten art, is a dish that usually involves the pairing of raw fish and rice, sometimes served in a seaweed wrapped roll with other additional ingredients.
The most notable roll in America during the early twenty first century was the California Roll, a combination of, often imitation, crab meat, avocado, and cucumber.
Sushi restaurants gained popularity at such rapid pace that the ahi tuna, one of the most popular among the fishes used to make these dishes, nearly went extinct until an international treaty limited their fishing.
The tuna, however, is not the fish of importance here.
We concern ourselves most, in this case, with salmon.
\\

Salmon is a wonderful fish that can live in both fresh water or salt water and will migrate between oceans and rivers with the seasons.
It also was, at the time of our story, around the year 2029 CE, one of the less expensive and more accessible fish sold both for sushi and cooked consumption.
Following the California roll and the Spicy Tuna roll, Salmon did, in fact, make up the third most popular fish to make sushi from, and, unlike the large ahi tuna which could take years to grow in the vast ocean, the farming of salmon for human consumption was a well practiced profession by those seeking to make a quick profit, or at least a quicker profit than an attempt at farming tuna would have provided.
\\

It was in the farming of this salmon that things began to get interesting.
At the first week of August, a Chilean aquaculturist by the name of Jose Soto reported that his stock were experiencing a series of symptoms unknown to him previously, and, soon later, all perished in a most unexpected death.
Not much would have been though of this event if it wasn't within the week, on a day known now as O Day, the twenty sixth of August in the year Two Tousand and Twenty Nine of the common era, that people began noticing that some of them were showing strange symptoms, mainly the fizziness of blood, as though they were experiencing decompression sickness.
If you've never gone scuba diving, as most people hadn't at the time, decompression sickness is something that can happen if you rise from a very deep depth up to a shallow one, from a higher pressure zone to a lower one, rapidly enough that your blood decides it's the ripe time to fizz up like a soft drink.
The symptom was being noticed in individuals who had not, not recently anyway, risen up through a change in pressure, and rightfully caused quite a stir.
Most of those who exibited this symptom soon died of it in a most painful fashon.
\\

We do not claim to know how the University of Michigan managed to link this event, which did not stop spreading until several weeks after it was first discovered, to the consumption of salmon raised in Mr. Soto's salmon farms several weeks prior.
What we do claim to know is what most academic and medical journals agree was the case.
Somehow, most likely due to the measures taken to prevent Mr. Soto's stock of salmon from dying to traditional diseases, a virus was born in his farms.
This virus had a few unique properties.
The first was that once infected with it, your DNA was altered to continue production of it, much like the HIV virus.
Since it became a part of its host, conventional measures traditionally used to get rid of such an intruder weren't at all effective, and the symptoms its presence, notably the fizzing of one's blood, didn't appear until several weeks after it entered one's system.
\\

It seemed to be the case that Mr. Soto's farm wasn't the only one with salmon that ultimatly shared the fate of his.
Atlantic salmon hacheries in Norway, Russia, Canada, and Scottland also noticed similar patterns to those noticed by Mr. Soto.
As result, <illness>, what this virus was ultimately named, was widespread throughout the world.
\\

The spread of <illness> caused a few interesting social changes.
It should first be noted that while salmon was less expensive than the ahi tuna, it was still much more costly than meat and poltry, a pound of the fish averaging about twice the mininum hourly wage in America at the time.
This lead to most of the affected individuals to be of a social class with some expendable funds, and those of the less well of seemed primarily without traces of <illness> in their systems.
\\

Before we mention the next of these social changes, this one being, in the authors opinion, the more fascinating, it would be wise to introduce that the researchers at Michigan discovered before they identified Mr. Soto's farm.
The <illness> virus did something to one's body that caused it to slowly alter the chemical structure of one's blood until the fizzy reaction took place.
If one were to get a transfusion of untainted blood, however, they could postpone the symptom for up to three days at a time, depending on the amount transfused and the physical health of the infected.
It became immediately quite common for individuals untainted by <illness> to sell quantaties of their \textit{clean blood} to those who needed it.
The selling of blood, however, is nothing new or interesting; individuals have been `donating` blood plasma for reaserch and medicine, often in exchange for some monitary compensation, for years.
What became unique about this was the shift of social and societial groups to bring people of similar blood type together.
\\

For some reason unknown to your poor author, blood harvested and kept until needed seemed to lack the ability to postponed <illness> for as long as blood fresh from another's veins.
Neighborhoods and social circles began shifting to a point where those with Type A blood could frequently be found with others of blood Type A, and the same with Type B.
While none with <illness> could be considered fortunate, those of blood Type AB did have the luxury of being able to accept transfusions from either group, and while those untainted with Type O could donate widely, they were often encouraged to stick with their fellow Type O since, as a group, they were more scarce and could only receive from each other.
\\

The RhD status (the + or - associated with the ABO), while certainly important, didn't find its way into the greater social selectiveness, as one might expect.
It would be common for those of types, for example, A+ and A- to live and socialize with each other quite frequently, such as in the instance of <main>(A+) and Jake(A-).
As I did above, and have been doing up to this point in our history, people began to introduce themselves to strangers featuring their blood type.
In our previous chapter, for example, it was clear that Roland was no stranger to <main> and Jake.
Roland resided just two doors down on Maple St.
Most of Maple St., at this time in history, was inhabited by those who possessed some sort of Type A blood, and it wasn't infrequent for exchanges such as the booze-for-blood to take place.
\\

There did, after, a few years, come some progress in the mitigation of <illness>.
A Californian pharmacedtical company, <pharm> developed an injection that if taken daily, would perform as though a small infusion of untainted blood were present.
This injection, <daily pill>, wasn't inexpensive though.
Most insurance plans wouldn't cover <daily pill>, since the drug cost about the equivalent to a new car annually, so the majority of people were content to pay their associates for the lifeblood that kept them alive.
After all of the mess made to patent policy in the late twentieth century, the government was powerless to attempt to intervene here, despite <illness>'s declaration as a national emergency.
\\

<pharma> wasn't just sitting over in their Bay-Area office raking in the dough for <daily pill>, or so those living in the area at the time might say.
<main> knew they were working on a slightly longer-term solution, something that could be taken monthly or even annually, and he knew this because that's exactly what he had been hired to work on after his graduate program.
\\

<main> would be one of the researchers in a group attempting to extend the effectiveness of <daily pill> first to a two-day remedy, and hopefully to more following that.
He had done a wonderful interview, at <pharm>'s Palo Alto HQ, with the lead researcher on this project, a Dr. Jean Reynolds, who had been a major contributor to the <cancer drug> project many years ago.
The opportunity to work with Dr. Reynolds was a top reason for <main>'s interest in <pharm>, beyond the prestige of working at a company as established as <pharm> and living in the San Francisco Bay Area where the weather was always perfect, and Dr. Reynolds had promised <main> that his acceptance into the lab had nothing to do with <main>'s relation to <father>.
\\

In all, <main> was quite enthusiastic for the next stage of his life, and now that we've, without too much distraction, laid out the necessary information for you, the esteemed reader of this fine work, to understand the motivations surrounding our characters, we will proceed, with haste, back into our story as <main> and Jake move on to this next, exciting, stage of their lives.
\\

\chapter{}

This portion of our history will focus on the means by which our heroes got from point A to point B.
Much can be said of these two points, for the journey from point A to point B is a legendary one quite often referenced in modern literature and discussion.
Few realize, however, the origin of these A and B points.
In our attempt to this history complete, we spent considerable effort in finding our readers everything required to fully appreciate this archaic idiom.
\\

It was told that the first use of the phrase ``go from point A to point B'' was done by Edward of Woodstock, also known as the Black Prince.
An English Monarch.
It has been recorded, and we found a photograph of the recording to confirm this, that Edward instructed at one point a servant to go on a set of errands.
This servant, being surprisingly literate for his position, recorded his orders on a sheet of paper.
Atop this sheet lay a rough outline of the palace and had a series of dots labeled with letters among it.
After receiving his orders, this servant, whose name seems to have been forgotten by the sands of time, was to go immedietaly from point A to point B in order to bring a letter written by Edward to some individual, whose identity has also been lost.
This was the first recorded instance of the phrase, in English, ``point A to point B'' being used.
\\

We have managed to trace this term further, back to the ancient Greeks.
Alexander the Great, a rather good general, was the first known user of the term, though, being Greek, it was more about point $\alpha$ and point $\beta$.
In his military maps, Alexander laid out the field in a grid with horizontal lines being labeled with letters and vertical ones being labeled with other letters.
It could be, for example, that Rome was at point $\gamma\kappa$ or the enemies residing within the square whose bottom corner lay at the intersection of $\theta\nu$.
Alexander would often arrange his maps such that the Greek troops resided in the bottom left corner, at $\alpha\alpha$ while their for lay somewhere in the middle of the map.
In a traditional battle, some batallion of pike men would advance, thus, towards the center going from the initial position of $\alpha\alpha$ to $\beta\beta$.
The frequency with which such a move occurred caused the Greeks to shorten the terminology, so such a manoever was labeled simply from $\alpha$ to $\beta$.
\\

This was, as we have determined, the first instance of a point A and point B referring to two distinct locations.
We have, in our research, noted a prior instance where which the term could have originated.
The ancient Hebrews had a language of their own, and in this Hebrew language, counting numbers used the same symbol as letters.  Now, the first two letters in the Hebrew alphabet were $\aleph$ (pronounced ``aleph'') and $\beth$ (pronounced ``bet''), and these two symbols could also, depending on context, be interpreted as being equivelant to our 1 and 2 symbols.
It is easy to understand that one could go from $\aleph$ to $\beth$ simply by increasing the amount of something from one to two, or any sort of increment.
This, we believe, was definitely the first time one might go from point A to point B; incrementing in Hebrew.
\\

In our case, however, we find that simply going from point A to point B isn't enough to describe the journey from Maple St. all the way to the lodgings arranged for <main> and Jake in Mountain View.
There were a few intermediary points, each of which we'll discuss in the necessary detail.

We'll begin, then, at 235 Maple St.  Having sufficiently packed their belongings, <main> and Jake made their way out from the apartment, which was still filled with boxes of stuff of which <main>'s parents would later be accompanying some movers to get, to one of the university's bus stops.
From there, they boarded one of the free university busses, on which there were a few undergrads, as they made their way to the cetneral transit hub where a slightly less free bus, the tickets having been paid for days prior, waited to drive <main>, Jake, and the three score other students making their way to the airport to the airport.
This part of the journey was quite uneventful.
<main> sat to Jake's left in a pair of seats on right side of the middle of the bus, and both of them read the books they had each brought for the journey.
Both the boys were fan of fantasy novels, so <main> had with him a few of Pratchett's \textit{Diskworld} books while Jake read a novel based on Dumas's \textit{The Three Musketeers}, but by an American author from Minnesota who framed it in a fantasy setting.
Jake was adamant that this novel was his favorite of all time, and after finishing some chapters, even having read the series with which this book was the first several time, he continued to end some chapters by leaning his head back and muttering ``god I love this book'' to himself.
\\

Once the bus reached the airport, our friends made their way over to the terminal.
Knowing that much of their belongings wouldn't make it to California for many days, they both had bags to check, which they did without considerable difficulty.
The queue for the security checkpoint was long, but there was enough time alotted before the flight that it was no matter, and by the time <main> and Jake ultimately reached their gate, thirty minutes lay between them and the boarding time for the flight.
One interesting phenomenon about airports is the percentage of people who choose to wear outfits depicting the logo of athletic teams.
At this time, neither <main> nor Jake had any sort of athletic appareal on, but they were both keen to notice, and discuss, just how many people walked by with verious football, baseball, and hockey teams' logos on their shirts, pants, hats, socks, and even, in one unfortuantely seen case, underware.
These observations weren't all that the boys had before they managed to board the flight, though.
Each of them spent a bit of money, on sandwitches, tuna for <main> and turkey for Jake, with which to call ``lunch''.
\\

The actual boarding of the plain was farely uneventful.
Jake ended up boarding first, since his seat was closer to the back of the flight, and <main> entered with a later group who's seats were closer to the middle.
While the two could have attempted to arrange to sit together, the companies employing both of them had bought each his respective ticket, and no coordination here was done between their corporate travel agents.
Jake ended up seated in the isle next to a portly gentleman in his mid fifties wearing buisness attire.
This man was no fun, as he took a sleeping pill after reaching his seat and said nothing to Jake the whole ride, but this proved no problem, for it let Jake continue in with his book; an experience he loved every minute of.
\\

<main>, while also in an isle seat, had a much more exciting and arguably slightly more enjoyable time, for across the isle from him was a girl.
About twenty five years of age, this individual had shoulder-length brown hair, wide eyes which seemed to indicate curiosity and interest, and a nose featuring an ever so slightly upward turn at the end which <main> found extreamly cute.
\\

``I see that's a Pratchett you're reading'' begin the stranger shortly after the flight-safety-presentation concluded, ``I loved those books when I was an undergrad.
Which of his characters do you find you like the most?
I always had trouble deciding between Vimes and Granny Whetherwax.''
\\

At this time, <main> had only read a few of these famous comedic fantasy works, so while he had experienced both the captain of the watch and the old witch mentioned by his cross-isle companion, the best answer <main> had was the one he uttered, ``Death is pretty great.''
\\

Those around the two who happened to be listening mostly understood that Death was, in these novels, a most spleanded character and a great answer, but the older lady sitting to <main>'s right produced an audible ``hmph'' and turned to look out the window to her right.
Noticing this, as they were no doubt intended, the two both giggled a bit, noticed the other giggling, smiled a bit more, without initially stopping the giggle, and, upon noticing this, blurted in sync, ``I'm''.
Both stopped there, noticing, once again, what was happening, and <main> raised his hand with a ``you first.''
His companion, anticipating this move that any gentleman would make, did not match <main> in declaration of order, and waited for her turn where she, as requested, noted ``I'm <romance>, (A+)'' followed by a raise of her eyebrows indicating that <main should continue.
\\

After <main> took his turn to introduce himself, the two spoke a bit more on the subject of Prathett's novels, a topic <romance> was quite fond of and <main> enjoyed substantially.
Following that, they ventured into the subject of their personal lives.
<main> noted that he had recently graduated with his Pharm D while <romance> let him know about her recent graduation from law school at the in-state university rival to <main>'s.
A joke was made by <main> that grad students didn't really participate in all the athletic rivalries, and <romance> sarcastically agreed; apparently she did her undergrad at the same university as her law school.

The old saying goes that ``time flies when you're having fun'', and it seems that time flew even faster than the jet plain, for it seemed all too soon when the plain made its decent in to the SFO airport.
<main> and <romance> exchanged contact cards, and after disboarding the flight, <romance> walked off while <main> awaited Jake at the gate.

The final leg of the journey to point B was no trouble at all.
After retrieving their checked baggage at the baggage claim, where <main> noted that he didn't see <romance> at all, the two took the BART over to the Milbray Caltrain station where they switched over to a train that took them to downtown Mountain View from which they walked to the lodging that Jakes's company had provided.
While the company didn't really practice housing randoms, Jake requested, from the ``relocation specialist'' a flat for two, and the specialist incorrectly assumed that Jake wanted the second bedroom for some sort of child.
Ultimately, the two did reach the apartment, and, after a brief journey back into town for some dinner, which they got at a very nice, though slightly overpriced diner, the two retired, at last, for the evening.

And that, esteemed readers, is the journey <main> and Jake took from point A to point B.

\chapter*{Interlude}

We would like to present our utmost apologies, but at this time, we find it necessary to provide a bit of interruption for some history.
Now, yes, everything you've read up to this point has been some history or another, but we must now provide some commentary on that history that we neglected from the previous section.
\\

First, you must have noticed that we described the day following the flight with much less detail than what occurred before <main> and Jake left the airport; this was intentional.
You see, for <main> and Jake both, the day's climax was the flight itself, and following that was just a rush to get to sleep, for flights can be quite exhausting.
<main>, as you may surmise, had his mind mostly focused on <romance>, so the rest of his day was mostly spent thinking about her while his body advanced through the necessary steps to get to his destination, the bed in which he planned to, and did, sleep.
\\

There is something else of note we wish to comment on regarding that previous section which we think will aid in the production of a complete history.
While the diner <main> and Jake elected to eat at was certainly nice, had this taken place several years in the past, that would not at all have been their destination.
Mountain View was, for many years, the home of a restaurant named Sushi Tomi.
This overpriced Japanese location was known as one of the best sushi resurants in the San Francisco Bay Area (``the Bay'', or the area around the city of San Francisco including everything on the peninsula north of San Jose and the ``east bay'' up to Berkeley).
Were this taking place before 2029, the two would have surely made Sushi Tomi their destination, but for about a decade after <illness> entered our society, much of the world took away from eating fish when possible.
In America, the seafood market had reduced, during this time, from a multi-billion dollar annual market to one only a fraction of its former glory.
\\

It wasn't until the early 2040s when people, once again, began eating fish.
During the hiatus, many of the fish species that had previously been serious portions of the world's diet but were diminishing due to over-fishing had began to approach their former population, and most governments established treaties that limited the fishing of these fish species to a much more sustainable level.
Were this history being written by some fish lord as opposed to a human, <illness> would have been praised as a blessing for fish kind, since the only major casualties there occurred in production farms.
Sadly, for the fish, we are yet unaware of any such fish lords who would be able to produce their opinion of the time period, so we'll have to be content with our human perspective.
\\

With those notes down, I feel that I have provided sufficient history on the history to, once again, continue following our heroes through their time in the Bay.
\\

\chapter{}

In America then, as with today, legislation regarding corporate benefits was always met with scrutiny by lobbiests and whose who believed that government should meddle less with individuals' lives rather than more, so few companies offered very nice relocation packages.
Jake, however, did not have a job lined up at most companies.
Jake was going to be working at Super Motors.
\\

Despite its name, which sounded as cheesy then as it probably does now, should the idiom persist, Super Motors a top producer of self-driving car technology.
In the year 2018, engineers at Super Motors, just a small startup at the time, wrote a RFC (request for comments) document outlining an open standard for an open self-driving car standard and api.
The idea was that any manufacturer could design a car that fit the specifications outlined in the RFC and the software that Super Motors produced, and published in an open-source manner, would work to provide a functional self-driving vehical.
\\

Super Motors made the bulk of their finances in a few ways.
Their most visible source of revenue were the cars they sold under the ``Super'' brand.
As they released their open standard, Super also introduced to the market the first vehical to use their software.
The ``Super One'' was trendy looking car at a price that was competitive for its value.
Immediately, people everywhere recognized the One driving around with Super Motor's logo, a siloet of a caped man flying with a fist forward, just different enough from the way Superman would in the comics as to avoid copyright complaints.
While many other brands began to produce cars adhering to the Super Standard, as it had been nicknamed by the media, Super brand cars were known as being the most pure and reliable in accordance to the standard.
\\

In addition to selling full cars, Super sold, to other auto manufacturers, many of the sensors and computer hardware they included in their Super brand offerings.
While the Super software worked through video recording equipment primarily, the type of cameras used and the hardware used to interface with the mechanical parts was expensive and difficult to produce unless done so at scale.
Some of the large auto companies, most notably those in Detroit, had no need for these products, but independent brands would often produce the shells and designs themselves while purchasing their computers and sensors directly from Super.
\\

The final and greatest source of revenue for them was an auditing process they performed on cars that followed the standard.
Many companies lined up to use the open-sourced software Super produced, but several of the cars produced by those companies either had design flaws in the hardware or electrical system.
If a manufacturer was serious about selling a vehical with Super software on the market, they were sure to get their cars Super-approved, a certification that cost the manufacturer a tax per vehical sold but allowed them to market the car successfully and add a trendy decal with Super's logo to their models.
\\

Jake would be working on their ``ethical decisions'' software engineering team.
Imagine that you are a self-driving car.
Driving down a mountain highway, you turn a sharp corner and see that directly in front of you are two people, a mother and a child, walking in the middle of the road.
The only way to avoid fatally hitting the child nd colliding with the mother as well would be to drive off the cliff, potentially killing the driver.
This pseudo-realistic scenario and many like it aren't the sort that should cause a Super car to immediately shut down to due lack of ethical decision software, so the team Jake was going to join was developing a new version of the advanced ethics engine to handle such situations.
\\

Apparently, people skilled in this area were widly sought after in industry, and Jake had recently completed a dissertaion on the topic, so Super had him set up with a very great relocation package that included the aid of an agent who would take Jake and those he wished to share lodging with, <main> in this case, around to several of the apartment compelxes that had available units.
Jake saw no reason to forfit such a bennefit or to waste time, so the morning after arriving in the Bay, <main> and Jake made their hunt for housing.
\\

The day began as any day should after flying from the east coast to California.
<main> woke up three hours earlier than he had set his alarm for, and after an additioal hour of attempted sleeping, decided to go for a run.
The run was pleasant, for the area was rather flat and the late spring weather perfect.
Following the run, <main> stopped at a local market to grab some breakfast cereal and milk which he left on the mainroom table as he took a morning shower.
By the time <main> had finished his shower, Jake was already sitting at the table eating a bowl of cerial with his right hand as he perused the itinerary the relocation agent had left him with his left.
Lizz (B-), or so the agent had been named, would be meeting the two outside their temporary accomodation in about an hour's time, and from there they would all travel around through Mountain View, Redwood City, Menlo Park and finally Palo Alto (in that order).
\\

Lizz arrived at the perscribed time.
She was driving a dark green Super Three, a mid-sized sport-utility vehicle, produced three years prior.
The first two locations visited were not far, one very close to the unit the two had as their temporary accomodation, which was nice due to its proximity to the downtown but had a subpar apartment community, while the other was a bit out of the way but very nice.
\\

The Redwood city apartmnet complexes were a bit more modern than the ones in Mountain View, having been built in the late 2010s, but much more notable to the two than the three flats they visited was teh taqueria Lizz took them to for lunch after.
If there was one thing that would never go out of style in the Bay, it's the Mexican food, which is still widly available there by the time of the publication of this work.
\\

After lunch, when the group was driving over to a location in Menlo Park, <main> recieved a message on his mobile that apparently came from <romance>.
\\

``Hey, how's your house hunting going?'' it read in a clearly casual manner.  <main> had mentioned that he'd be making the rounds while talking to <romance> on the flight, so it was a fine opening, he determined to himself.
\\

After waiting a few seconds, as to not seem too eager, <main> replied with what he thought was casual yet slightly humerous in tone, ``It's been going well.  The burritos in Redwood City are really good :P''.
For those of you who may not be familiar, the ``:P'' symbol is what was known as an ``emoji'' at the time.
When textual communications were still popular, these \textit{emoji} were used to imitate faces in messages and the emotions those faces would represent.
If you rotate this particular emoji ninty degrees clockwise, you can imagine how the colon would represent a face's eyes and the ``P'' a mouth with a toung sticking out; this emoji frequently accompanied jokes to signify such.
\\

About a minute later, <main> received a reply, ``you don't want to live in Redwood.  everyone there is old and boring'', to which <main> quickly shot back ``thanks for the advice.  Where're you staying?''
\\

At this time, Lizz had stopped at yet another apartment to check out.  This one seemed really old, though it was spacious.
<main> and Jake both appreciated the proximity to Menlo Park's quaint downtown area.
When the group took to the roads again, <main> had yet to receive another message from <romance>, and didn't so until after the group had explored the remaining location in the city. |  when <main> did eventually get this message, it was short and didn't feel at all conversational: ``Atherton, but you can't really rent here.''  <main> knew Atherton; it was a small town smashed between Menlo Park and Redwood City.
it also happened to be home of the most expensive zip-code in the country.
for those of you who may not be up-to-date on postal-history, zip-codes or \textit{postal-codes}, as they were sometimes called, were five-digit numbers that represented a region of space, usually the size of a small city, for which the postal service could easily send a letter initially.
often, zip-codes had little meaning outside of a postal or statistical context, they weren't even associated with election voting districts, though there is the famous example of Purdue university refusing to build a building taller than the first building on their campus within the same zip-code as that initial building while ignoring this rule across the street.
in this case, the city of Atherton had exactly one zip-code, numbered 94027 for those who are curious, and that zip-code shared the same boarders as the city itself.
\\

finally, the agent took them to a few locations in Palo Alto.  these were, by far, the most expensive units visited during the trip even though they were also among the oldest.  the cost, however, was justified, because <main> and Jake agreed to sign a lease at an apartment they enjoyed not too far from Sanford university's campus.
this particular apartment featured two bedrooms and two bathrooms, a configuration <main> and Jake had come accustomed too.
in addition to these, the unit had a rather large kitchen, with a \textit{newly renovated} set of granite counter-tops.
there was a main room large enough to fit a small dining table, a set of couches, and a TV.
the layout was quite nice as well.
if the unit was a rectangle wider at the base than the width, the kitchen and main room occupied the center from bottom to top, with the front door opening next to the kitchen at the bottom, and the main room separated not by a full wall but by a counter overlooking the sink on the kitchen-side.
to the left of the main room and kitchen, if you're standing as though you had just entered the flat, you would see a small hallway containing the laundry closet, one of the bathrooms and one of the bedrooms.
this was the bedroom that Jake would be occupying, its window facing away from the sunrise and its closet substantial.
to the right, from the same flat-entering perspective, was a door leading to the room <main> had selected.
this was a slightly larger room than Jake's, and the bathroom was directly connected, though the closet was no smaller than Jake's.
<main> had elected to pay a slightly higher portion of the rent in exchange for this larger lodging option.
for the location, Palo Alto being still, as it was years before, a very popular place, and in a type a neighborhood, the apartment was exactly what the two were looking for, so they elected to move in on the following day, which they did without much difficulty.
\\

\chapter*{interlude}

You may have noticed in your reading of this history some very significant detail that we've neglected.
now, we wish not to presume ourselves some authority on what is important and what is trivial, so here we follow some feedback we have received after our initial edition of this publication.
in the first edition, both the one directly previous in writing to this edition you're reading now, unless we've been lazy and forgotten to modify this passage in subsequent editions, and the first one we wrote on this topic, we described the process of the transfusions done for <illness> in detail when they occurred, which, given the nature of <illness> was daily.
some of our readers, we have been told, are not the most tollorant in the face of needles and blood.  some of our more squeamish readers have even written to us noting that our descriptions were so realistic that the thoughts of the situations made those readers experience nausea or, in the case of one fan who elected to handwrite us a letter in green ink, fainting.
because we wish to maintain our audience's goodwill, we have written a single description of the process and placed it in an appendix that will be shipping with some clearly marked versions of this work.
we hope that this is an acceptable solution to our readers and that they understand these transfusions did happen on a daily bases for our characters and that blood was often exchanged with those near them in the community as we saw at maple st.

\chapter{}

While we claim not to be time-wizards, we have, up to this point, described three sequential days, one of dining, one of travel, and one of searching.
These were certainly important days, as every day contains some sort of importance within it, but the days immediately following were less so.
We could discuss in detail how <main> and Jake spent hours looking through digital catalogues of items with which to furnish their new home, noting the serious contention between <main>'s yearning for the ease of non-stick pots while Jake begged to be allotted a set he could use high heat with, but we have chosen not too.
Instead, we will bring our history to a day nine in advance, the Monday in which <main> and Jake were set to start their professional careers.
\\

<main> began this day has he had his days during the past week.
Just as the sun rose, waking him up, <main> went for a quick run, listening, in this instance, to an album by a German band by the name of Gamma Ray since he liked starting the day with their ``Welcome'' intro track.
Following his run, <main> cooked for himself and ate a bowl of oatmeal.
The onboarding information suggested that wearing jeans would be fine at <pharm>, so <main> decided he'd spend his first day with a pair of his nice darker jeans and a light blue golf shirt.
<main> was planning on biking the three miles to his office, but since this was his first day and the location of office showers were still an unknown to him, today <main> opted to take a self-driving cab.
One of the moves Super had made initially after gaining popularity was joining up with a crowdsourced-cab company, based in San Francisco, to produce a service that allowed individuals to use their mobiles to hail self-driving cars which would pick them up and drive them to a prescribed destination.
While many people opted for these as their primary form of transportation, it still turned out to be more economical to own one's own car if more than just a daily commute was anticipated.
\\

The trip to work for <main> was uneventful, and <main> arrived right at 8:00, the time his onboarding information prescribed.
<pharm>'s headquarters office featured three buildings all of a similar style.
All of these buildings followed a smiliar old-style design where the exterior appeared to be little more than constant rows of windowed floors.
The coloring here featured extreamly reflective blue-grey windows and cement-colored accents between.
The buildings were arranged so the first one seen upon entering their driveway/parking-lot wasn't very tall, just three stories, but covered a very wide portion.
Facing the front door to this, you could see the two larger cylindrical towers that made up the other two buildings.
While <main> didn't really know all the stuff <pharm> could possibly need so much space for or what they were doing with all their employees, he knew he would be starting his journey in the flatter Building 1.
\\

The way an establishment chooses to shape the room seen immediately after entering the main doors can really very from location to location.
Places that don't expect many visitors or guests will usually have a smaller lobby with a ceiling no higher than the rooms it connects.
These rooms often serve the purpose of asking an individual ``are you sure you really have business here?''
Other places may have an extra story added to the lobby's ceiling height to give a sense of place.
Guests waiting in these rooms won't at all feel cramped, unless the rooms are very crowded.
Finally, a building may feature a large atrium at its enterence.
Atriums featuring coredors and internal-facing office windows were a popular architectural style when the <pharm> offices had been built, so of course their Building 1 featured such an atrium.
\\

As <main> entered the building, he was immediately impressed by the sense of open space he felt.
The atrium here was very large, its ceiling being also the buildings roof, a pointed one at the top of the building through which the sun and clouds could be seen, and its dimensions feeling as large as a regulation football field with the main enterence where a goal posts would lie.
Continuing this football analogy, along where the twenty yard line would be stood a four foot high partition made of glass.
In the center of this partition were two counters, peopled by red-shirt wearing physical security guards, and between these two counters were glass gates that would flap open as employees presented their credentials.
<pharm> employees eager to begin their work days were shuffling through these gates as though the practice had become second nature, but since <main> had yet to receive any credentials, he approached the left security counter and began to converse with one of the guards.


\end{document}
